\chapter{Crowdsourcing strategies in Pl@ntNet citizen based learning platform}
\label{chap:plantnet}
\enlargethispage{3\baselineskip}

\begin{keypointstwomargins}{Pl@ntNet}{-2cm}{-1cm}
        \textbf{Key points -- Crowdsourcing plant species}
        \begin{enumerate}[leftmargin=*]
        \item Aiding botanists in plant species identification is a challenging task. Species are often visually close and their identification requires expert knowledge.
        \item Pl@ntNet is a citizen science platform that allows users to upload images of plants and receive a list of possible species.
        \item The collaborative aspect of Pl@ntNet allows users to vote on the species they think are present in the image and contribute to new labeled data, which is then used to train a computer vision and help new identifications.
        \end{enumerate}

        \textbf{Contributions -- Exploration of Pl@ntNet label aggregation strategy}
        \begin{enumerate}[leftmargin=*,start=4]
        \item We release and evaluate the current Pl@ntNet label aggregation and compare it to other strategies.
        \item We release a subset of Pl@ntNet with images url and collected labels in the South Western European Flora of more than $6$ million observations and $800$ thousand users in a large-scale classification setting.
        \item We discuss how to integrate the current model's predictions in the votes aggregation. This is a challenging task due to the iterative aspect of Pl@ntNet: the current data helps train the next generation of models iteratively.
        \end{enumerate}
\end{keypointstwomargins}


\section{Crowdsourcing for plant species identification}

\subsection{Presenting the voting interface}

\subsection{A step in a bigger pipeline}

\section{Pl@ntNet's label aggregation strategy}

\subsection{Presentation of the algorithm}

\subsection{Presenting a subset of Pl@ntNet to evaluate the current strategy}

\section{Integrating model predictions in the aggregation}

\subsection{Possible strategies}

\subsection{Can we trust our current predicted probabilities?}

\section{Conclusion}